---
title: "Homework 3 - Functions I"
author: "Runxiang Liu"
date: "21/2/2023"
output:
  md_document:
    toc: yes
    variant: markdown_github
  html_document:
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

# Homework 3 - Functions I

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Write a function that takes a single numerical vector and returns three values, the minimum number, the median, and the maximum number of the vector. Test your function using the month column of the flights dataset.

### loading dataset
```{r}
library(nycflights13)
library(tidyverse)
```

### construct min_med_max function
```{r}
min_med_max <- function(x) {
  c(min(x), median(x), max(x))
}

min_med_max(flights$month)
```
## Explain your reasoning for choosing your function’s name in the previous question.
I chose the name min_med_max because it is descriptive of what the function does. It takes a vector and returns the minimum, median, and maximum values of the vector.

## Write a function that categorizes a numerical variable in the flights data into four categories.
```{r}
categorize_time <- function(data, column) {
  data %>% select(column) %>%
    mutate(time = case_when(
      column >= 500 & column <= 1159 ~ "Morning",
      column >= 1200 & column <= 1659 ~ "Afternoon",
      column >= 1700 & column <= 2059 ~ "Evening",
      column >= 2100 | column <= 459 ~ "Night"
    ))
}

result<-categorize_time(flights, 'dep_time')
head(result,10)
```
## Explain your reasoning for choosing your function’s name in the previous question.
I chose the name categorize_time because it is descriptive of what the function does. It takes a data object and a column name and returns a new column with the values categorized into four categories.

## Write a function that calculates the median of all numeric variables in the flights dataset using a s`for` loop.
```{r}
flights_numeric_vars<-select_if(flights, is.numeric)
result.median <- 0

median_for <- function(data) {
  for (i in names(data)) {
    print(median(data[[i]], na.rm = TRUE))
  } 
}
median_for.result <- median_for(flights_numeric_vars)
```
## Explain your reasoning for choosing your function’s name in the previous question.
I chose the name median_for because it is descriptive of what the function does. It takes a data object and returns the median of all numeric variables in the data object by using a for loop.




